---
title: "Diagnostic Report"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: cosmo
    highlight: espresso
params:
  vetting: ""
  coverage_data: ""
  site_data: ""
  country_name: ""
  site_output: ""
  averted_output: ""
  burden_output: ""
  dose_output: ""
  population: ""
  population_by_age: ""
---

```{r setup, include=FALSE, warning = FALSE, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message= FALSE)

vetting<- params$vetting
site_output<- params$site_output
averted_output<- params$averted_output
burden_output<- params$burden_output
coverage_data<- params$coverage_data
dose_output<- params$dose_output
site_data<- params$site_data
population <- params$population
population_by_age<- params$population_by_age
country_name<- params$country_name

pfprs<- readRDS('pfpr10plus_admins.rds')
source('diagnostic_report_functions.R')

```

This is a diagnostic report for `r country_name`.

# Vaccine Coverage

```{r vaccine coverage}
plot_vaccine_coverage(coverage_data, country_name = {{country_name}})
```

# Site file

## Intervention coverage

```{r intervention coverage}
plot_intvn_coverage(site_data)
```

## Cases and Deaths

```{r cases and deaths}
cases_deaths_diagnostic(site_data)
```

## Admin units {.tabset}

### Moderate-to-High transmission sites

```{r}
pfprs |>
  filter(run_model == TRUE,
         country == {{country_name}})

```

### Low transmission sites

```{r}
pfprs |>
  filter(run_model == FALSE,
         country == {{country_name}})

```

## Site level cases + deaths per FVP {.tabset}

### Cases
```{r case comparison}

plot_case_site_comparison(dose_output$site_doses)


```

### Deaths

```{r death comparison}

plot_death_site_comparison(dose_output$site_doses)

```


## Population distribution {.tabset}

### Population over time

```{r population}

ggplot(data = population, mapping= aes(x= year, y= value))+
  geom_line() +
  plotting_theme +
  labs(title = ('Total population over time'),
       subtitle = {{country_name}})
       
```

###    Population at beginning and end of simulation 

```{r}
population_by_age<- data.table(population_by_age) |> filter(age_from < 6)

under_5<- population_by_age |>
  group_by(year) |>
  summarise(value = sum(value))

p<- ggplot(data = under_5, mapping= aes(x= year, y= value))+
  geom_line() +
  plotting_theme +
  labs(title = ('Population under 5 over time'),
       subtitle = {{country_name}})
       
p
```
# Incidence

## Incidence over time {.tabset}

### rts3-rts4-default 

```{r} 
incidence_over_time(burden_output$by_year,  
                    scenario= 'malaria-rts3-rts4-default', 
                     site_data, 
                     coverage_data) 
```




### r3-r4-default 
```{r incidence_time_r4}
incidence_over_time(burden_output$by_year,  
                    scenario= 'malaria-r3-r4-default',
                     site_data,
                     coverage_data) 
```


## Incidence over age {.tabset}


### rts3-rts4-default 

```{r} 
incidence_over_age(burden_output$by_age,
                     scenario= 'malaria-rts3-rts4-default', 
                     coverage_data) 
```



### r3-r4-default 

```{r incidence_age_r4}
incidence_over_age(burden_output$by_age,  
                    scenario= 'malaria-r3-r4-default', 
                    coverage_data) 

```

## Incidence rate over time {.tabset}

### rts3-rts4-default
```{r} 
incidence_rate_over_time(burden_output$by_year, 
scenario= 'malaria-rts3-rts4-default', 
coverage_data) 
```



### r3-r4-default
```{r ir_time_r4}
incidence_rate_over_time(burden_output$by_year,  
                     scenario= 'malaria-r3-r4-default',
                     coverage_data) 
```


## Incidence rate over age  {.tabset}



### rts3-rts4-default 

```{r}
incidence_rate_over_age(burden_output$by_age, 
                     scenario= 'malaria-rts3-rts4-default',
              coverage_data) 


``` 


### r3-r4-default 

```{r ir_age_r4_default}
incidence_rate_over_age(burden_output$by_age,  
                     scenario= 'malaria-r3-r4-default', 
                     coverage_data) 
```



## Cases averted over time {.tabset}


### rts3-rts4-default 

```{r}
cases_averted_over_time(averted_output$by_year,  
                         scenario= 'malaria-rts3-rts4-default', 
                         country_name = {{country_name}}) 


```


### r3-r4-default 

```{r cases_av_time_r4}
 cases_averted_over_time(averted_output$by_year,  
                         scenario= 'malaria-r3-r4-default', 
                         country_name = {{country_name}}) 

```





## Cases averted over age {.tabset}


### rts3-rts4-default 

```{r cases_age_rts} 
cases_averted_over_age(averted_output$by_age,  
                         scenario= 'malaria-rts3-rts4-default', 
                         country_name = {{country_name}}) 
```


### r3-r4-default 
```{r cases_age_r3} 
cases_averted_over_age(averted_output$by_age,  
                        scenario= 'malaria-r3-r4-default', 
                         country_name = {{country_name}}) 
```



# Deaths

## Deaths over time {.tabset}

### rts3-rts4-default 
```{r} 
deaths_over_time(burden_output$by_year, 
                     scenario= 'malaria-rts3-rts4-default',
                     coverage_data) 

``` 

 

### r3-r4-default 

```{r}
deaths_over_time(burden_output$by_year, 
                    scenario= 'malaria-r3-r4-default', 
                     coverage_data) 
```




## Deaths over age {.tabset}


### rts3-rts4-default 

```{r}
deaths_over_age(burden_output$by_age, 
                scenario= 'malaria-r3-r4-default',
                coverage_data) 

```

## Deaths averted over time {.tabset}


### rts3-rts4-default

```{r}
deaths_averted_over_time(averted_output$by_year, 
                         scenario= 'malaria-rts3-rts4-default', 
                        country_name = {{country_name}}) 
 
``` 



### r3-r4-default 

```{r} 
  deaths_averted_over_time(averted_output$by_year,
                          scenario= 'malaria-r3-r4-default', 
                          country_name = {{country_name}}) 
                        
```



## Deaths averted over age {.tabset}

### rts3-rts4-default 

```{r} 
deaths_averted_over_age(averted_output$by_age,  
                         scenario= 'malaria-rts3-rts4-default', 
                         country_name = {{country_name}}) 
```



### r3-r4-default

```{r} -->
deaths_averted_over_age(averted_output$by_age,  
                        scenario= 'malaria-r3-r4-default',
                         country_name = {{country_name}}) 
```


# DALYs

## DALYs over time {.tabset}


### rts3-rts4-default 

```{r} -->
 dalys_over_time(burden_output$by_year,  
                     scenario= 'malaria-rts3-rts4-default', 
                    coverage_data) 
 
```


### r3-r4-default 

```{r} 
dalys_over_time(burden_output$by_year, 
                     scenario= 'malaria-r3-r4-default', 
                     coverage_data) 
```



## DALYs averted over age {.tabset}


### rts3-rts4-default 

```{r} 
dalys_averted_over_age(averted_output$by_age, 
                         scenario= 'malaria-rts3-rts4-default', 
                         country_name = {{country_name}}) 
```

### r3-r4-default 

```{r} 
dalys_averted_over_age(averted_output$by_age, 
                         scenario= 'malaria-r3-r4-default', 
                         country_name = {{country_name}}) 
```

## DALYs averted over time {.tabset}


### rts3-rts4-default 

```{r}
dalys_averted_over_time(averted_output$by_year, 
                         scenario= 'malaria-rts3-rts4-default', 
                         country_name = {{country_name}}) 
```


### r3-r4-default 

```{r}
dalys_averted_over_time(averted_output$by_year, 
                         scenario= 'malaria-r3-r4-default', 
                         country_name = {{country_name}}) 
```
