---
title: "Diagnostic Report"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: cosmo
    highlight: espresso
params:
  vetting: ""
  coverage_data: ""
  site_data: ""
  country_name: ""
  site_output: ""
  averted_output: ""
  burden_output: ""
  dose_output: ""
  population: ""
  population_by_age: ""
---

```{r setup, include=FALSE, warning = FALSE, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message= FALSE)

vetting<- params$vetting
site_output<- params$site_output
averted_output<- params$averted_output
burden_output<- params$burden_output
coverage_data<- params$coverage_data
dose_output<- params$dose_output
site_data<- params$site_data
population <- params$population
population_by_age<- params$population_by_age
country_name<- params$country_name

pfprs<- readRDS('pfpr10plus_admins.rds')
```

This is a diagnostic report for `r country_name`.

# Vaccine Coverage

```{r vaccine coverage}
plot_vaccine_coverage(coverage_data, country_name = {{country_name}})
```

# Site file

## Intervention coverage

```{r intervention coverage}
plot_intvn_coverage(site_data)
```

## Cases and Deaths

```{r cases and deaths}
cases_deaths_diagnostic(site_data)
```

## Admin units {.tabset}

### Moderate-to-High transmission sites

```{r}
pfprs |>
  filter(run_model == TRUE,
         country == {{country_name}})

```

### Low transmission sites

```{r}
pfprs |>
  filter(run_model == FALSE,
         country == {{country_name}})

```

## Site level cases + deaths per FVP {.tabset}

### Cases
```{r case comparison}

plot_case_site_comparison(dose_output$site_doses)


```

### Deaths

```{r death comparison}

plot_death_site_comparison(dose_output$site_doses)

```


## Population distribution {.tabset}

### Population over time

```{r population}

ggplot(data = population, mapping= aes(x= year, y= value))+
  geom_line() +
  plotting_theme +
  labs(title = ('Total population over time'),
       subtitle = {{country_name}})
       
```

###    Population at beginning and end of simulation 

```{r}
population_by_age<- data.table(population_by_age) |> filter(age_from < 6)

under_5<- population_by_age |>
  group_by(year) |>
  summarise(value = sum(value))

p<- ggplot(data = under_5, mapping= aes(x= year, y= value))+
  geom_line() +
  plotting_theme +
  labs(title = ('Population under 5 over time'),
       subtitle = {{country_name}})
       
p
```
# Incidence

## Incidence over time {.tabset}

<!-- ### rts3-default -->
<!-- # ```{r} -->
<!-- # incidence_over_time(burden_output$by_year,  -->
<!-- #                     scenario= 'malaria-rts3-default', -->
<!-- #                     site_data, -->
<!-- #                     coverage_data) -->
<!-- # ``` -->
<!-- #  -->
<!-- # ### rts3-bluesky -->
<!-- #  -->
<!-- # ```{r} -->
<!-- # incidence_over_time(burden_output$by_year,  -->
<!-- #                     scenario= 'malaria-rts3-bluesky', -->
<!-- #                     site_data, -->
<!-- #                     coverage_data) -->
<!-- # ``` -->

<!-- ### rts3-rts4-default -->

<!-- # ```{r} -->
<!-- # incidence_over_time(burden_output$by_year,  -->
<!-- #                     scenario= 'malaria-rts3-rts4-default', -->
<!-- #                     site_data, -->
<!-- #                     coverage_data) -->
<!-- # ``` -->

<!-- ### rts3-rts4-bluesky -->

<!-- # ```{r} -->
<!-- # incidence_over_time(burden_output$by_year,  -->
<!-- #                     scenario= 'malaria-rts3-rts4-bluesky', -->
<!-- #                     site_data, -->
<!-- #                     coverage_data) -->
<!-- # ``` -->


<!-- ### r3-default -->

<!-- ```{r incidence_time_r3} -->
<!-- incidence_over_time(burden_output$by_year,  -->
<!--                     scenario= 'malaria-r3-default', -->
<!--                     site_data, -->
<!--                     coverage_data) -->
<!-- ``` -->

### r3-bluesky

```{r incidence_time_r3_bluesky}
incidence_over_time(burden_output$by_year, 
                    scenario= 'malaria-r3-bluesky',
                    site_data,
                    coverage_data)
```

<!-- ### r3-r4-default -->

<!-- ```{r incidence_time_r4} -->
<!-- incidence_over_time(burden_output$by_year,  -->
<!--                     scenario= 'malaria-r3-r4-default', -->
<!--                     site_data, -->
<!--                     coverage_data) -->
<!-- ``` -->

### r3-r4-bluesky

```{r incidence_time_r4_bluesky}
incidence_over_time(burden_output$by_year, 
                    scenario= 'malaria-r3-r4-bluesky',
                    site_data,
                    coverage_data)
```



## Incidence over age {.tabset}

<!-- ### rts3-default -->

<!-- ```{r} -->
<!-- incidence_over_age(burden_output$by_age,  -->
<!--                     scenario= 'malaria-rts3-default', -->
<!--                     coverage_data) -->
<!-- ``` -->

<!-- ### rts3-bluesky -->

<!-- # ```{r} -->
<!-- # incidence_over_age(burden_output$by_age,  -->
<!-- #                     scenario= 'malaria-rts3-bluesky', -->
<!-- #                     coverage_data) -->
<!-- # ``` -->

<!-- ### rts3-rts4-default -->

<!-- # ```{r} -->
<!-- # incidence_over_age(burden_output$by_age,  -->
<!-- #                     scenario= 'malaria-rts3-rts4-default', -->
<!-- #                     coverage_data) -->
<!-- # ``` -->

<!-- ### rts3-rts4-bluesky -->

<!-- # ```{r} -->
<!-- # incidence_over_age(burden_output$by_age,  -->
<!-- #                     scenario= 'malaria-rts3-rts4-bluesky', -->
<!-- #                     coverage_data) -->
<!-- # ``` -->

<!-- ### r3-default -->

<!-- ```{r incidence_age_r3} -->
<!-- incidence_over_age(burden_output$by_age,  -->
<!--                     scenario= 'malaria-r3-default', -->
<!--                     coverage_data) -->
<!-- ``` -->

### r3-bluesky

```{r incidence_age_r3_bluesky}
incidence_over_age(burden_output$by_age, 
                    scenario= 'malaria-r3-bluesky',
                    coverage_data)
```

<!-- ### r3-r4-default -->

<!-- ```{r incidence_age_r4} -->
<!-- incidence_over_age(burden_output$by_age,  -->
<!--                     scenario= 'malaria-r3-r4-default', -->
<!--                     coverage_data) -->
<!-- ``` -->

### r3-r4-bluesky

```{r incidence_age_r4_bluesky}
incidence_over_age(burden_output$by_age, 
                    scenario= 'malaria-r3-r4-bluesky',
                    coverage_data)
```

## Incidence rate over time {.tabset}

<!-- ### rts3-default -->

<!-- ```{r} -->
<!-- incidence_rate_over_time(burden_output$by_year,  -->
<!--                     scenario= 'malaria-rts3-default', -->
<!--                     coverage_data = coverage_data) -->
<!-- ``` -->

<!-- ### rts3-bluesky -->

<!-- ```{r} -->
<!-- incidence_rate_over_time(burden_output$by_year,  -->
<!--                     scenario= 'malaria-rts3-bluesky', -->
<!--                     coverage_data) -->
<!-- ``` -->

<!-- ### rts3-rts4-default -->

<!-- # ```{r} -->
<!-- # incidence_rate_over_time(burden_output$by_year,  -->
<!-- #                     scenario= 'malaria-rts3-rts4-default', -->
<!-- #                     coverage_data) -->
<!-- # ``` -->

<!-- ### rts3-rts4-bluesky -->

<!-- ```{r} -->
<!-- incidence_rate_over_time(burden_output$by_year,  -->
<!--                     scenario= 'malaria-rts3-rts4-bluesky', -->
<!--                     coverage_data) -->
<!-- ``` -->

<!-- ### r3-default -->

<!-- ```{r ir_time_r3} -->
<!-- incidence_rate_over_time(burden_output$by_year,  -->
<!--                     scenario= 'malaria-r3-default', -->
<!--                     coverage_data = coverage_data) -->
<!-- ``` -->

### r3-bluesky

```{r ir_time_r3_bluesky}
incidence_rate_over_time(burden_output$by_year, 
                    scenario= 'malaria-r3-bluesky',
                    coverage_data)
```

<!-- ### r3-r4-default -->

<!-- ```{r ir_time_r4} -->
<!-- incidence_rate_over_time(burden_output$by_year,  -->
<!--                     scenario= 'malaria-r3-r4-default', -->
<!--                     coverage_data) -->
<!-- ``` -->

### r3-r4-bluesky

```{r ir_time_r4_bluesky}
incidence_rate_over_time(burden_output$by_year, 
                    scenario= 'malaria-r3-r4-bluesky',
                    coverage_data)
```

## Incidence rate over age  {.tabset}

<!-- ### rts3-default -->

<!-- ```{r} -->
<!-- incidence_rate_over_age(burden_output$by_age,  -->
<!--                     scenario= 'malaria-rts3-default',  -->
<!--                     coverage_data) -->
<!-- ``` -->

<!-- ### rts3-bluesky -->
<!-- # ```{r} -->
<!-- # incidence_rate_over_age(burden_output$by_age,  -->
<!-- #                     scenario= 'malaria-rts3-bluesky', -->
<!-- #                     coverage_data) -->
<!-- # ``` -->

<!-- ### rts3-rts4-default -->
<!-- # ```{r} -->
<!-- # incidence_rate_over_age(burden_output$by_age,  -->
<!-- #                     scenario= 'malaria-rts3-rts4-default', -->
<!-- #                     coverage_data) -->
<!-- # ``` -->

<!-- ### rts3-rts4-bluesky -->
<!-- # ```{r} -->
<!-- # incidence_rate_over_age(burden_output$by_age,  -->
<!-- #                     scenario= 'malaria-rts3-rts4-bluesky', -->
<!-- #                     coverage_data) -->
<!-- # ``` -->

<!-- ### r3-default -->
<!-- ```{r ir_age_r3} -->
<!-- incidence_rate_over_age(burden_output$by_age,  -->
<!--                     scenario= 'malaria-r3-default',  -->
<!--                     coverage_data) -->
<!-- ``` -->

### r3-bluesky
```{r ir_r3_age_bluesky}
incidence_rate_over_age(burden_output$by_age, 
                    scenario= 'malaria-r3-bluesky',
                    coverage_data)
```

<!-- ### r3-r4-default -->
<!-- ```{r ir_age_r4_default} -->
<!-- incidence_rate_over_age(burden_output$by_age,  -->
<!--                     scenario= 'malaria-r3-r4-default', -->
<!--                     coverage_data) -->
<!-- ``` -->

### r3-r4-bluesky
```{r ir_age_r4_bluesky}
incidence_rate_over_age(burden_output$by_age, 
                    scenario= 'malaria-r3-r4-bluesky',
                    coverage_data)
```


## Cases averted over time {.tabset}

<!-- ### rts3-bluesky -->

<!-- ```{r} -->
<!-- cases_averted_over_time(averted_output$by_year,  -->
<!--                         scenario= 'malaria-rts3-bluesky', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### rts3-default -->

<!-- # ```{r} -->
<!-- # cases_averted_over_time(averted_output$by_year,  -->
<!-- #                         scenario= 'malaria-rts3-default', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

<!-- ### rts3-rts4-bluesky -->

<!-- # ```{r} -->
<!-- # cases_averted_over_time(averted_output$by_year,  -->
<!-- #                         scenario='malaria-rts3-rts4-bluesky', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

<!-- ### rts3-rts4-default -->

<!-- ```{r} -->
<!-- cases_averted_over_time(averted_output$by_year,  -->
<!--                         scenario= 'malaria-rts3-rts4-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

### r3-bluesky

```{r cases_av_r3_bluesky}
cases_averted_over_time(averted_output$by_year, 
                        scenario= 'malaria-r3-bluesky',
                        country_name = {{country_name}})
```

<!-- ### r3-default -->

<!-- ```{r cases_av_r3_default} -->
<!-- cases_averted_over_time(averted_output$by_year,  -->
<!--                         scenario= 'malaria-r3-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

### r3-r4-bluesky

```{r cases_av_r3_bluesky1}
cases_averted_over_time(averted_output$by_year, 
                        scenario='malaria-r3-r4-bluesky',
                        country_name = {{country_name}})
```

<!-- ### r3-r4-default -->

<!-- ```{r cases_av_time_r4} -->
<!-- cases_averted_over_time(averted_output$by_year,  -->
<!--                         scenario= 'malaria-r3-r4-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->


## Cases averted over time per dose {.tabset}

<!-- ### rts3-bluesky -->

<!-- ```{r} -->
<!-- cases_averted_per_dose(dose_output$country_doses,  -->
<!--                         scenario= 'malaria-rts3-bluesky', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### rts3-default -->

<!-- # ```{r} -->
<!-- # cases_averted_per_dose(dose_output$country_doses,  -->
<!-- #                         scenario= 'malaria-rts3-default', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

<!-- ### rts3-rts4-bluesky -->

<!-- # ```{r} -->
<!-- # cases_averted_per_dose(dose_output$country_doses,  -->
<!-- #                         scenario='malaria-rts3-rts4-bluesky', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

<!-- ### rts3-rts4-default -->

<!-- # ```{r} -->
<!-- # cases_averted_per_dose(dose_output$country_doses,  -->
<!-- #                         scenario= 'malaria-rts3-rts4-default', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

### r3-bluesky

```{r cases_av_dose_r3_bluesky}
cases_averted_per_dose(dose_output$country_doses, 
                        scenario= 'malaria-r3-bluesky',
                        country_name = {{country_name}})
```

<!-- #### r3-default -->

<!-- ```{r cases_av_dose_r3_default} -->
<!-- cases_averted_per_dose(dose_output$country_doses,  -->
<!--                         scenario= 'malaria-r3-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

### r3-r4-bluesky

```{r cases_av_dose_r4_bluesky}
cases_averted_per_dose(dose_output$country_doses, 
                        scenario='malaria-r3-r4-bluesky',
                        country_name = {{country_name}})
```

<!-- ### r3-r4-default -->

<!-- ```{r case_av_r4_default} -->
<!-- cases_averted_per_dose(dose_output$country_doses,  -->
<!--                         scenario= 'malaria-r3-r4-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->


## Cases averted over time per FVP {.tabset}

<!-- ### rts3-bluesky -->

<!-- ```{r} -->
<!-- cases_averted_per_fvp(dose_output$country_doses,  -->
<!--                         scenario= 'malaria-rts3-bluesky', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### rts3-default -->

<!-- # ```{r} -->
<!-- # cases_averted_per_fvp(dose_output$country_doses,  -->
<!-- #                         scenario= 'malaria-rts3-default', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

<!-- ### rts3-rts4-bluesky -->

<!-- ```{r} -->
<!-- cases_averted_per_fvp(dose_output$country_doses,  -->
<!--                         scenario='malaria-rts3-rts4-bluesky', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### rts3-rts4-default -->

<!-- # ```{r} -->
<!-- # cases_averted_per_fvp(dose_output$country_doses,  -->
<!-- #                         scenario= 'malaria-rts3-rts4-default', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

### r3-bluesky

```{r cases_av_r3_fvp}
cases_averted_per_fvp(dose_output$country_doses, 
                        scenario= 'malaria-r3-bluesky',
                        country_name = {{country_name}})
```

<!-- ### r3-default -->

<!-- ```{r cases_Av_fvp_r3_default} -->
<!-- cases_averted_per_fvp(dose_output$country_doses,  -->
<!--                         scenario= 'malaria-r3-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

### r3-r4-bluesky

```{r cases_av_r4_bluesky1}
cases_averted_per_fvp(dose_output$country_doses, 
                        scenario='malaria-r3-r4-bluesky',
                        country_name = {{country_name}})
```

<!-- #### r3-r4-default -->

<!-- ```{r} -->
<!-- cases_averted_per_fvp(dose_output$country_doses,  -->
<!--                         scenario= 'malaria-r3-r4-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->


## Cases averted over age {.tabset}

<!-- ### rts3-bluesky -->

<!-- ```{r} -->
<!-- cases_averted_over_age(averted_output$by_age,  -->
<!--                         scenario= 'malaria-rts3-bluesky', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### rts3-default -->

<!-- # ```{r} -->
<!-- # cases_averted_over_age(averted_output$by_age,  -->
<!-- #                         scenario= 'malaria-rts3-default', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

<!-- ### rts3-rts4-bluesky -->

<!-- # ```{r} -->
<!-- # cases_averted_over_age(averted_output$by_age,  -->
<!-- #                         scenario='malaria-rts3-rts4-bluesky', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

<!-- ### rts3-rts4-default -->

<!-- ```{r} -->
<!-- cases_averted_over_age(averted_output$by_age,  -->
<!--                         scenario= 'malaria-rts3-rts4-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->



### r3-bluesky

```{r}
cases_averted_over_age(averted_output$by_age, 
                        scenario= 'malaria-r3-bluesky',
                        country_name = {{country_name}})
```

<!-- ### r3-default -->

<!-- ```{r} -->
<!-- cases_averted_over_age(averted_output$by_age,  -->
<!--                         scenario= 'malaria-r3-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

### r3-r4-bluesky

```{r}
cases_averted_over_age(averted_output$by_age, 
                        scenario='malaria-r3-r4-bluesky',
                        country_name = {{country_name}})
```

<!-- ### r3-r4-default -->
<!-- ```{r} -->
<!-- cases_averted_over_age(averted_output$by_age,  -->
<!--                         scenario= 'malaria-r3-r4-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->



# Deaths

## Deaths over time {.tabset}

<!-- ### rts3-default -->

<!-- ```{r} -->
<!-- deaths_over_time(burden_output$by_year,  -->
<!--                     scenario= 'malaria-rts3-default', -->
<!--                     coverage_data) -->
<!-- <!-- ``` 

<!-- ### rts3-bluesky -->

<!-- # ```{r}
<!-- # deaths_over_time(burden_output$by_year,
<!-- #                     scenario= 'malaria-rts3-bluesky',
<!-- #                     coverage_data)
<!-- # ```

<!-- ### rts3-rts4-default -->

<!-- # ```{r} -->
<!-- # deaths_over_time(burden_output$by_year,  -->
<!-- #                     scenario= 'malaria-rts3-rts4-default', -->
<!-- #                     coverage_data) -->
<!-- # ``` -->

<!-- ### rts3-rts4-bluesky -->

<!-- # ```{r} -->
<!-- # deaths_over_time(burden_output$by_year,  -->
<!-- #                     scenario= 'malaria-rts3-rts4-bluesky', -->
<!-- #                     coverage_data)
<!-- # ```

<!-- ### r3-default -->
<!-- ```{r} -->
<!-- deaths_over_time(burden_output$by_year, -->
<!--                     scenario= 'malaria-r3-default', -->
<!--                     coverage_data) -->
<!-- ``` -->

### r3-bluesky

```{r}
deaths_over_time(burden_output$by_year, 
                    scenario= 'malaria-r3-bluesky',
                    coverage_data)
```

<!-- ### r3-r4-default -->

<!-- ```{r} -->
<!-- deaths_over_time(burden_output$by_year,  -->
<!--                     scenario= 'malaria-r3-r4-default', -->
<!--                     coverage_data) -->
<!-- ``` -->

### r3-r4-bluesky
```{r}
deaths_over_time(burden_output$by_year, 
                    scenario= 'malaria-r3-r4-bluesky',
                    coverage_data)
```



## Deaths over age {.tabset}

<!-- ### rts3-default -->

<!-- # ```{r} -->
<!-- # deaths_over_age(burden_output$by_age,  -->
<!-- #                     scenario= 'malaria-rts3-default', -->
<!-- #                     coverage_data) -->
<!-- # ``` -->

<!-- ### rts3-bluesky -->

<!-- # ```{r} -->
<!-- # deaths_over_age(burden_output$by_age,  -->
<!-- #                     scenario= 'malaria-rts3-bluesky', -->
<!-- #                     coverage_data) -->
<!-- # ``` -->

<!-- ### rts3-rts4-default -->

<!-- ```{r} -->
<!-- deaths_over_age(burden_output$by_age,  -->
<!--                     scenario= 'malaria-rts3-rts4-default', -->
<!--                     coverage_data) -->
<!-- ``` -->

<!-- ### rts3-rts4-bluesky -->

<!-- # ```{r} -->
<!-- # deaths_over_age(burden_output$by_age,  -->
<!-- #                     scenario= 'malaria-rts3-rts4-bluesky', -->
<!-- #                     coverage_data) -->
<!-- # ``` -->

<!-- ### r3-default -->

<!-- ```{r} -->
<!-- deaths_over_age(burden_output$by_age,  -->
<!--                     scenario= 'malaria-r3-default', -->
<!--                     coverage_data) -->
<!-- ``` -->

<!-- ### rts3-bluesky -->

<!-- ```{r} -->
<!-- deaths_over_age(burden_output$by_age,  -->
<!--                     scenario= 'malaria-r3-bluesky', -->
<!--                     coverage_data) -->
<!-- ``` -->

<!-- ### rts3-rts4-default -->

<!-- # ```{r} -->
<!-- # deaths_over_age(burden_output$by_age,  -->
<!-- #                     scenario= 'malaria-r3-r4-default', -->
<!-- #                     coverage_data) -->
<!-- # ``` -->

### r3-r4-bluesky

```{r}
deaths_over_age(burden_output$by_age, 
                    scenario= 'malaria-r3-r4-bluesky',
                    coverage_data)
```


## Deaths averted over time {.tabset}
<!-- ### rts3-bluesky -->

<!-- ```{r} -->
<!-- deaths_averted_over_time(averted_output$by_year,  -->
<!--                         scenario= 'malaria-rts3-bluesky', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### rts3-default -->

<!-- # ```{r} -->
<!-- # deaths_averted_over_time(averted_output$by_year,  -->
<!-- #                         scenario= 'malaria-rts3-default', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

<!-- ### rts3-rts4-bluesky -->

<!-- ```{r} -->
<!-- deaths_averted_over_time(averted_output$by_year,  -->
<!--                         scenario='malaria-rts3-rts4-bluesky', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### rts3-rts4-default -->

<!-- ```{r} -->
<!-- deaths_averted_over_time(averted_output$by_year,  -->
<!--                         scenario= 'malaria-rts3-rts4-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

### r3-bluesky

```{r}
deaths_averted_over_time(averted_output$by_year, 
                        scenario= 'malaria-r3-bluesky',
                        country_name = {{country_name}})
```

<!-- ### rts3-default -->

<!-- # ```{r} -->
<!-- # deaths_averted_over_time(averted_output$by_year,  -->
<!-- #                         scenario= 'malaria-r3-default', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

### r3-r4-bluesky

```{r}
 deaths_averted_over_time(averted_output$by_year,
                         scenario='malaria-r3-r4-bluesky',
                         country_name = {{country_name}})
```

<!-- ### r3-r4-default -->

<!-- ```{r} -->
<!--  deaths_averted_over_time(averted_output$by_year, -->
<!--                          scenario= 'malaria-r3-r4-default', -->
<!--                          country_name = {{country_name}}) -->
<!-- ``` -->



## Deaths averted over time per dose {.tabset}

<!-- ### rts3-bluesky -->

<!-- # ```{r} -->
<!-- # deaths_averted_per_dose(dose_output$country_doses,  -->
<!-- #                         scenario= 'malaria-rts3-bluesky', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

<!-- ### rts3-default -->

<!-- ```{r} -->
<!-- deaths_averted_per_dose(dose_output$country_doses,  -->
<!--                         scenario= 'malaria-rts3-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### rts3-rts4-bluesky -->

<!-- # ```{r} -->
<!-- # deaths_averted_per_dose(dose_output$country_doses,   -->
<!-- #                         scenario='malaria-rts3-rts4-bluesky', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

<!-- ### rts3-rts4-default -->

<!-- ```{r} -->
<!-- deaths_averted_per_dose(dose_output$country_doses,  -->
<!--                         scenario= 'malaria-rts3-rts4-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

### r3-bluesky

```{r}
deaths_averted_per_dose(dose_output$country_doses, 
                        scenario= 'malaria-r3-bluesky',
                        country_name = {{country_name}})
```

<!-- ### r3-default -->

<!-- ```{r} -->
<!-- deaths_averted_per_dose(dose_output$country_doses, -->
<!--                         scenario= 'malaria-r3-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

### r3-r4-bluesky

```{r}
deaths_averted_per_dose(dose_output$country_doses, 
                        scenario='malaria-r3-r4-bluesky',
                        country_name = {{country_name}})
```

<!-- ### r3-r4-default -->

<!-- ```{r} -->
<!-- deaths_averted_per_dose(dose_output$country_doses,  -->
<!--                         scenario= 'malaria-r3-r4-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->


## Deaths averted over time per fvp {.tabset}

<!-- ### rts3-bluesky -->

<!-- # ```{r} -->
<!-- # deaths_averted_per_fvp(dose_output$country_doses,  -->
<!-- #                         scenario= 'malaria-rts3-bluesky', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

<!-- ### rts3-default -->

<!-- ```{r} -->
<!-- deaths_averted_per_fvp(dose_output$country_doses,  -->
<!--                         scenario= 'malaria-rts3-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### rts3-rts4-bluesky -->

<!-- ```{r} -->
<!-- deaths_averted_per_fvp(dose_output$country_doses,   -->
<!--                         scenario='malaria-rts3-rts4-bluesky', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### rts3-rts4-default -->

<!-- # ```{r} -->
<!-- # deaths_averted_per_fvp(dose_output$country_doses, -->
<!-- #                         scenario= 'malaria-rts3-rts4-default', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

### r3-bluesky

```{r}
deaths_averted_per_fvp(dose_output$country_doses, 
                        scenario= 'malaria-r3-bluesky',
                        country_name = {{country_name}})
```

<!-- ### r3-default -->

<!-- ```{r} -->
<!-- deaths_averted_per_fvp(dose_output$country_doses,  -->
<!--                         scenario= 'malaria-r3-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

### r3-r4-bluesky

```{r}
deaths_averted_per_fvp(dose_output$country_doses, 
                        scenario='malaria-r3-r4-bluesky',
                        country_name = {{country_name}})
```

<!-- ### r3-r4-default -->

<!-- ```{r} -->
<!-- deaths_averted_per_fvp(dose_output$country_doses,  -->
<!--                         scenario= 'malaria-r3-r4-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

## Deaths averted over age {.tabset}

<!-- #### rts3-bluesky -->

<!-- ```{r} -->
<!-- deaths_averted_over_age(averted_output$by_age,  -->
<!--                         scenario= 'malaria-rts3-bluesky', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->


<!-- ### rts3-default -->

<!-- ```{r} -->
<!-- deaths_averted_over_age(averted_output$by_age,  -->
<!--                         scenario= 'malaria-rts3-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### rts3-rts4-bluesky -->

<!-- ```{r} -->
<!-- deaths_averted_over_age(averted_output$by_age,  -->
<!--                         scenario='malaria-rts3-rts4-bluesky', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### rts3-rts4-default -->

<!-- # ```{r} -->
<!-- # deaths_averted_over_age(averted_output$by_age,  -->
<!-- #                         scenario= 'malaria-rts3-rts4-default', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

### r3-bluesky

```{r}
deaths_averted_over_age(averted_output$by_age, 
                        scenario= 'malaria-r3-bluesky',
                        country_name = {{country_name}})
```

<!-- ### r3-default -->

<!-- ```{r} -->
<!-- deaths_averted_over_age(averted_output$by_age,  -->
<!--                         scenario= 'malaria-r3-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

### r3-r4-bluesky

```{r}
deaths_averted_over_age(averted_output$by_age, 
                        scenario='malaria-r3-r4-bluesky',
                        country_name = {{country_name}})
```

<!-- ### r3-r4-default -->

<!-- ```{r} -->
<!-- deaths_averted_over_age(averted_output$by_age,  -->
<!--                         scenario= 'malaria-r3-r4-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->


# DALYs

## DALYs over time {.tabset}

<!-- ### rts3-default -->

<!-- ```{r} -->
<!-- dalys_over_time(burden_output$by_year,  -->
<!--                     scenario= 'malaria-rts3-default', -->
<!--                     coverage_data) -->
<!-- ``` -->

<!-- ### rts3-bluesky -->

<!-- # ```{r} -->
<!-- # dalys_over_time(burden_output$by_year,  -->
<!-- #                     scenario= 'malaria-rts3-bluesky', -->
<!-- #                     coverage_data) -->
<!-- # ``` -->

<!-- ### rts3-rts4-default -->

<!-- ```{r} -->
<!-- dalys_over_time(burden_output$by_year,  -->
<!--                     scenario= 'malaria-rts3-rts4-default', -->
<!--                     coverage_data) -->
<!-- ``` -->

<!-- ### rts3-rts4-bluesky -->

<!-- ```{r} -->
<!-- dalys_over_time(burden_output$by_year,  -->
<!--                     scenario= 'malaria-rts3-rts4-bluesky', -->
<!--                     coverage_data) -->
<!-- ``` -->

<!-- ### r3-default -->

<!-- ```{r} -->
<!-- dalys_over_time(burden_output$by_year,  -->
<!--                     scenario= 'malaria-r3-default', -->
<!--                     coverage_data) -->
<!-- ``` -->

### r3-bluesky

```{r}
dalys_over_time(burden_output$by_year, 
                    scenario= 'malaria-r3-bluesky',
                    coverage_data)
```

<!-- ### r3-r4-default -->

<!-- ```{r} -->
<!-- dalys_over_time(burden_output$by_year,  -->
<!--                     scenario= 'malaria-r3-r4-default', -->
<!--                     coverage_data) -->
<!-- ``` -->

### r3-r4-bluesky

```{r}
dalys_over_time(burden_output$by_year, 
                    scenario= 'malaria-rts3-rts4-bluesky',
                    coverage_data)
```




## DALYs averted over age {.tabset}
<!-- ### rts3-bluesky -->

<!-- ```{r} -->
<!-- dalys_averted_over_age(averted_output$by_age,  -->
<!--                         scenario= 'malaria-rts3-bluesky', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### rts3-default -->

<!-- # ```{r} -->
<!-- # dalys_averted_over_age(averted_output$by_age,  -->
<!-- #                         scenario= 'malaria-rts3-default', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

<!-- ### rts3-rts4-bluesky -->

<!-- ```{r} -->
<!-- dalys_averted_over_age(averted_output$by_age,  -->
<!--                         scenario='malaria-rts3-rts4-bluesky', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### rts3-rts4-default -->

<!-- ```{r} -->
<!-- dalys_averted_over_age(averted_output$by_age,  -->
<!--                         scenario= 'malaria-rts3-rts4-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

### r3-bluesky

```{r}
dalys_averted_over_age(averted_output$by_age, 
                        scenario= 'malaria-r3-bluesky',
                        country_name = {{country_name}})
```

<!-- ### rts3-default -->

<!-- ```{r} -->
<!-- dalys_averted_over_age(averted_output$by_age,  -->
<!--                         scenario= 'malaria-r3-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

### r3-r4-bluesky

```{r}
dalys_averted_over_age(averted_output$by_age, 
                        scenario='malaria-r3-r4-bluesky',
                        country_name = {{country_name}})
```

<!-- ### r3-r4-default -->

<!-- ```{r} -->
<!-- dalys_averted_over_age(averted_output$by_age,  -->
<!--                         scenario= 'malaria-r3-r4-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->



## DALYs averted over time {.tabset}


<!-- ### rts3-bluesky -->

<!-- ```{r} -->
<!-- dalys_averted_over_time(averted_output$by_year,  -->
<!--                         scenario= 'malaria-rts3-bluesky', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### rts3-default -->

<!-- ```{r} -->
<!-- dalys_averted_over_time(averted_output$by_year,  -->
<!--                         scenario= 'malaria-rts3-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### rts3-rts4-bluesky -->

<!-- # ```{r} -->
<!-- # dalys_averted_over_time(averted_output$by_year,  -->
<!-- #                         scenario='malaria-rts3-rts4-bluesky', -->
<!-- #                         country_name = {{country_name}}) -->
<!-- # ``` -->

<!-- ### rts3-rts4-default -->

<!-- ```{r} -->
<!-- dalys_averted_over_time(averted_output$by_year,  -->
<!--                         scenario= 'malaria-rts3-rts4-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->



<!-- ## Averted by dose {.tabset} -->


<!-- ### Cases -->

<!-- ```{r} -->
<!-- cases_averted_per_dose(averted_output$by_year, country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### Deaths -->
<!-- ```{r} -->
<!-- deaths_averted_per_dose(averted_output$by_year, country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### DALYs -->
<!-- ```{r} -->
<!-- dalys_averted_per_dose(averted_output$by_year, country_name = {{country_name}}) -->
<!-- ``` -->



#### r3-bluesky

```{r}
dalys_averted_over_time(averted_output$by_year, 
                        scenario= 'malaria-r3-bluesky',
                        country_name = {{country_name}})
```

<!-- #### r3-default -->

<!-- ```{r} -->
<!-- dalys_averted_over_time(averted_output$by_year,  -->
<!--                         scenario= 'malaria-r3-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->

#### r3-r4-bluesky

```{r}
dalys_averted_over_time(averted_output$by_year, 
                        scenario='malaria-r3-r4-bluesky',
                        country_name = {{country_name}})
```

<!-- #### r3-r4-default -->

<!-- ```{r} -->
<!-- dalys_averted_over_time(averted_output$by_year,  -->
<!--                         scenario= 'malaria-r3-r4-default', -->
<!--                         country_name = {{country_name}}) -->
<!-- ``` -->



<!-- ## Averted by dose {.tabset} -->


<!-- ### Cases -->

<!-- ```{r} -->
<!-- cases_averted_per_dose(averted_output$by_year, country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### Deaths -->
<!-- ```{r} -->
<!-- deaths_averted_per_dose(averted_output$by_year, country_name = {{country_name}}) -->
<!-- ``` -->

<!-- ### DALYs -->
<!-- ```{r} -->
<!-- dalys_averted_per_dose(averted_output$by_year, country_name = {{country_name}}) -->
<!-- ``` -->
