---
title: 'VIMC diagnostic report: country'
output:
  html_document: 
    theme: united
    highlight: tango
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(scene)
library(ggpubr)
library(data.table)
options(scipen = 999)
site<- site_data

# source plotting code for report
lapply(list.files('functions/', full.names = T), source, local= knitr::knit_global())

# read in parameters



```

## VIMC country-level diagnostic report


This is a diagnostic report for VIMC outputs for `r iso3c`, `r site_data$sites$country[1]`. 
The description for this model run is `r description`. The scenario ran was `r scenario`. The population size of this model run was `r population`. The burn-in time was `r burnin` years. For this run, quick_run was `r quick_run` .

Total cases in the country in WMR 2020 were `r format_number(cases_wmr_2020)`.
Total modelled cases in 2020 were `r format_number(cases_mod_2020)`.

Up to 2100, `r percent_cases_averted_2100` % of cases were averted by vaccine.
 
Cases averted per 100,000 vaccinated were: `r format_number(outcomes_averted$cases_averted)`.

Deaths averted per 100,000 vaccinated were: `r format_number(outcomes_averted$deaths_averted)`.

DALYs averted per 100,000 vaccinated were: `r format_number(outcomes_averted$dalys_averted)`.



## Vaccine coverage specified for scenario
```{r inputs}

plot_vaccine_coverage(coverage_data)
intro_yr<- min(coverage_data[coverage!= 0, year])

```

### Coverage of other interventions 
```{r intervention coverage, fig.height=10, fig.width= 15}
plot_interventions_combined(
  interventions = site_data$interventions,
  population = site_data$population,
  group_var = c("country", "name_1"),
  include = c("itn_use", "itn_input_dist", "tx_cov", "smc_cov", "pmc_cov", "rtss_cov"),
  labels = c("ITN usage", "ITN model input", "Treatment","SMC", "PMC", "RTSS")
)


```


### Site file cases and deaths
```{r cases_deaths, echo=FALSE}

cases_deaths_diagnostic(site_data)


```


## Country population (VIMC)
```{r pop, echo=FALSE}

population_diagnostic_vimc(population_data)


```

## Modelled outputs

```{r population, echo=FALSE, fig.height=10, fig.width= 15}
population_diagnostic_model(agg_output, pg= 1, intro_yr = intro_yr, summary = T)


population_diagnostic_model(processed_output, pg= 1, intro_yr = intro_yr)
population_diagnostic_model(processed_output, pg= 2, intro_yr = intro_yr)
population_diagnostic_model(processed_output, pg= 3, intro_yr = intro_yr)
population_diagnostic_model(processed_output, pg= 4, intro_yr = intro_yr)


```

# Incident cases
```{r incident cases, echo=FALSE, fig.height=10, fig.width= 15}
incident_cases_diagnostic(agg_output, pg= 1, intro_yr = intro_yr, summary = T)

scaling_diagnostic(agg_output)

incident_cases_diagnostic(processed_output, pg= 1, intro_yr = intro_yr)
incident_cases_diagnostic(processed_output, pg= 2, intro_yr = intro_yr)
incident_cases_diagnostic(processed_output, pg= 3, intro_yr = intro_yr)
incident_cases_diagnostic(processed_output, pg= 4, intro_yr = intro_yr)


```

#   Incidence rate 
```{r incidence rate, echo = FALSE, fig.height=10, fig.width= 10}
incidence_rate_diagnostic(agg_output, pg= 1, intro_yr = intro_yr, summary = T)

  
incidence_rate_diagnostic(processed_output, pg= 1, intro_yr = intro_yr)
incidence_rate_diagnostic(processed_output, pg= 2, intro_yr = intro_yr)
incidence_rate_diagnostic(processed_output, pg= 3, intro_yr = intro_yr)
incidence_rate_diagnostic(processed_output, pg= 4, intro_yr = intro_yr)

```

# Deaths

```{r deaths, echo=FALSE, fig.height=10, fig.width= 15}
mortality_diagnostic(agg_output, pg= 1, intro_yr = intro_yr, summary = T)

mortality_diagnostic(processed_output, pg= 1, intro_yr = intro_yr)
mortality_diagnostic(processed_output, pg= 2, intro_yr = intro_yr)
mortality_diagnostic(processed_output, pg= 3, intro_yr = intro_yr)
mortality_diagnostic(processed_output, pg= 4, intro_yr = intro_yr)

```

# Mortality rate 
```{r mort rate, echo=FALSE, fig.height=10, fig.width= 15}
mortality_rate_diagnostic(agg_output, pg= 1, intro_yr = intro_yr, summary = T)

  
mortality_rate_diagnostic(processed_output, pg= 1, intro_yr = intro_yr)
mortality_rate_diagnostic(processed_output, pg= 2, intro_yr = intro_yr)
mortality_rate_diagnostic(processed_output, pg= 3, intro_yr = intro_yr)
mortality_rate_diagnostic(processed_output, pg= 4, intro_yr = intro_yr)

```

# DALYs
```{r dalys, echo = FALSE, fig.height=10, fig.width= 15}
daly_diagnostic(agg_output, pg = 1, intro_yr = intro_yr, summary = T)


daly_diagnostic(processed_output, pg = 1, intro_yr = intro_yr)
daly_diagnostic(processed_output, pg = 2, intro_yr = intro_yr)
daly_diagnostic(processed_output, pg = 3, intro_yr = intro_yr)
daly_diagnostic(processed_output, pg = 4, intro_yr = intro_yr)

```


# Cases averted by age

```{r cases averted, echo =FALSE, fig.height=10, fig.width= 15}
plot_cases_averted(intvn_output, baseline_output)

```

