---
title: 'VIMC diagnostic report: site'
output:
  html_document: 
    theme: united
    highlight: tango
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(scene)
library(ggpubr)
library(data.table)

site<- site_data
# source plotting code for report
lapply(list.files('functions/', full.names = T), source, local= knitr::knit_global())


```

## VIMC site-level diagnostic report

This is a diagnostic report for VIMC outputs for `r site_name`, `r ur`. The EIR for this site is `r site_data$eir$eir[[1]]`. The description for this model run is `r description`. The scenario ran was `r scenario`. The population size of this model run was `r population`. The burn-in time was `r burnin` years. For this run, quick_run was `r quick_run` .


Cases averted per 100,000 fully vaccinated in this site up to 2040 = `r formatC(key_outcomes$cases_averted[grep("2040",key_outcomes$timeframe)], format="f", big.mark=",", digits=0)`

Cases averted per 100,000 fully vaccinated in this site up to 2100 = `r formatC(key_outcomes$cases_averted[grep("2100",key_outcomes$timeframe)], format="f", big.mark=",", digits=0)`

Deaths averted per 100,000 fully vaccinated in this site up to 2100 = `r formatC(key_outcomes$deaths_averted[grep("2100",key_outcomes$timeframe)], format="f", big.mark=",", digits=0)`.  

Total cases averted in this site over all years in the model are:
`r formatC(pull_tot_cases_averted(processed_output)[[1]]$cases_averted, format="f", big.mark=",", digits=0)`
and total deaths averted:
`r formatC(pull_tot_cases_averted(processed_output)[[1]]$deaths_averted, format="f", big.mark=",", digits=0)`

Total cases in the country in WMR 2020 were `r formatC(site_data$cases_deaths$wmr_cases[which(site_data$cases_deaths$year==2020)], format="f", big.mark=",", digits=0)`.

## Vaccine coverage specified for scenario

```{r inputs}

plot_vaccine_coverage(model_input)
intvns<- data.table(model_input$interventions)

intro_yr<- min(intvns[rtss_coverage!= 0 | r21_coverage!= 0, year])


ints<- melt(model_input$interventions, id.vars = 'year', measure.vars = c("itn_use", "itn_input_dist", "tx_cov", "smc_cov", "pmc_cov", "irs_cov", "rtss_cov"))

ggplot(data= ints)+
  geom_line(mapping = aes(x= year, y= value, color= variable))+
  labs(color= 'Intervention',
       y= 'Proportional coverage value',
       x=' Year',
       title = 'Intervention coverage over simulation period') +
  plotting_theme
```


# Doses delivered in raw model outputs

```{r doses}
plot_doses_delivered(raw_output)


```

<!-- # Plot mortality rates for VIMC inputs -->

<!-- ```{r mortality rate} -->

<!-- plotting_theme<- theme_bw(base_size = 12) + -->
<!--   theme( legend.position = 'bottom', -->
<!--          strip.text.x = element_text(size = rel(0.8)), -->
<!--          axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1.1),  -->
<!--          #axis.text.y = element_blank(), -->
<!--          text = element_text(family= 'Arial Narrow'), -->
<!--          axis.ticks.y= element_blank(),  -->
<!--          panel.grid.major = element_blank(), panel.grid.minor = element_blank())  -->



<!-- p1<- ggplot(data = site$demography, mapping = aes(x= age_upper, y= mortality_rate))+ -->
<!--   geom_point()+ -->
<!--   ylim(0, 1.2) + -->
<!--   plotting_theme + -->
<!--   labs(title= 'Site file mortality rate inputs (2000-2500))', -->
<!--        xlab= 'age', -->
<!--        ylab= 'mortality rate') -->


<!-- p2<-ggplot(data = mort, mapping = aes(x= age_to, y= value))+ -->
<!--   geom_point()+ -->
<!--   ylim(0, 1.2)+ -->
<!--   plotting_theme+ -->
<!--   labs(title= 'VIMC mortality rate inputs (2000-2100))', -->
<!--        xlab= 'age', -->
<!--        ylab= 'mortality rate') -->

<!-- ggarrange(p1, p2, ncol= 2) -->

<!-- ``` -->


# Site file diagnostics
# Prevalence 
# Site file inputs
```{r prevalence, echo=FALSE}

prevalence_diagnostic(site)


```
# Model outputs
```{r}
plot_pfpr_over_time(raw_output, intro_yr = intro_yr)
```

## Site file
```{r pop, echo=FALSE}

population_diagnostic(site)


```

## Modelled outputs

```{r population, echo=FALSE, fig.height=10, fig.width= 15}

population_diagnostic_model(agg_output, pg= 1, intro_yr = intro_yr, summary = T)


population_diagnostic_model(processed_output, pg= 1, intro_yr = intro_yr)
population_diagnostic_model(processed_output, pg= 2, intro_yr = intro_yr)
population_diagnostic_model(processed_output, pg= 3, intro_yr = intro_yr)
population_diagnostic_model(processed_output, pg= 4, intro_yr = intro_yr)


```

# Incident cases
```{r incident cases, echo=FALSE, fig.height=10, fig.width= 15}
incident_cases_diagnostic(agg_output, pg= 3, intro_yr = intro_yr, summary = T)

incident_cases_diagnostic(processed_output, pg= 1, intro_yr = intro_yr)
incident_cases_diagnostic(processed_output, pg= 2, intro_yr = intro_yr)
incident_cases_diagnostic(processed_output, pg= 3, intro_yr = intro_yr)
incident_cases_diagnostic(processed_output, pg= 4, intro_yr = intro_yr)


```

#   Incidence rate 
```{r incidence rate, echo = FALSE, fig.height=10, fig.width= 10}

incidence_rate_diagnostic(agg_output, pg = 1, intro_yr = intro_yr, summary = T)
  
incidence_rate_diagnostic(processed_output, pg= 1, intro_yr = intro_yr)
incidence_rate_diagnostic(processed_output, pg= 2, intro_yr = intro_yr)
incidence_rate_diagnostic(processed_output, pg= 3, intro_yr = intro_yr)
incidence_rate_diagnostic(processed_output, pg= 4, intro_yr = intro_yr)

```

# Deaths

```{r deaths, echo=FALSE, fig.height=10, fig.width= 15}

mortality_diagnostic(agg_output, pg = 1, intro_yr = intro_yr, summary = T)


mortality_diagnostic(processed_output, pg= 1, intro_yr = intro_yr)
mortality_diagnostic(processed_output, pg= 2, intro_yr = intro_yr)
mortality_diagnostic(processed_output, pg= 3, intro_yr = intro_yr)
mortality_diagnostic(processed_output, pg= 4, intro_yr = intro_yr)

```

# Mortality rate 
```{r mort rate, echo=FALSE, fig.height=10, fig.width= 15}
  mortality_rate_diagnostic(agg_output, pg= 1, intro_yr = intro_yr, summary = T)


mortality_rate_diagnostic(processed_output, pg= 1, intro_yr = intro_yr)
mortality_rate_diagnostic(processed_output, pg= 2, intro_yr = intro_yr)
mortality_rate_diagnostic(processed_output, pg= 3, intro_yr = intro_yr)
mortality_rate_diagnostic(processed_output, pg= 4, intro_yr = intro_yr)

```

# DALYs
```{r dalys, echo = FALSE, fig.height=10, fig.width= 15}
daly_diagnostic(agg_output, pg = 1, intro_yr = intro_yr, summary = T)

daly_diagnostic(processed_output, pg = 1, intro_yr = intro_yr)
daly_diagnostic(processed_output, pg = 2, intro_yr = intro_yr)
daly_diagnostic(processed_output, pg = 3, intro_yr = intro_yr)
daly_diagnostic(processed_output, pg = 4, intro_yr = intro_yr)

```


# Cases averted by age

```{r cases averted, echo =FALSE, fig.height=10, fig.width= 15}
plot_cases_averted(processed_output)

```

