---
title: "Diagnostic Report"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: cosmo
    highlight: espresso
params:
  vetting: ""
  coverage_data: ""
  site_data: ""
  country_name: ""
  site_output: ""
  dose_output: ""
  averted_output: ""
  burden_output: ""
---

```{r setup, include=FALSE, warning = FALSE, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message= FALSE)

vetting<- params$vetting
site_output<- params$site_output
averted_output<- params$averted_output
burden_output<- params$burden_output
coverage_data<- params$coverage_data
site_data<- params$site_data

pfprs<- readRDS('pfpr10plus_admins.rds')
```

This is a diagnostic report for `r country_name`.

# Vaccine Coverage

```{r vaccine coverage}
plot_vaccine_coverage(coverage_data, country_name = {{country_name}})
```

# Site file

## Intervention coverage

```{r intervention coverage}
plot_intvn_coverage(site_data)
```

## Cases and Deaths

```{r cases and deaths}
cases_deaths_diagnostic(site_data)
```

## Admin units {.tabset}

### Moderate-to-High transmission sites

```{r}
pfprs |>
  filter(run_model == TRUE,
         country == {{country_name}})

```

### Low transmission sites

```{r}
pfprs |>
  filter(run_model == FALSE,
         country == {{country_name}})

```

# Incidence

## Cases by scenario

```{r cases by scenario}
scenario_comparison_plot(output = averted_output$by_year, country_name = {{country_name}})
```

## Incidence over time {.tabset}

### malaria-rts3-default

```{r}
incidence_over_time(burden_output$by_year, 
                    scenario= 'malaria-rts3-default',
                    site_data,
                    coverage_data)
```

### malaria-rts3-bluesky

```{r}
incidence_over_time(burden_output$by_year, 
                    scenario= 'malaria-rts3-bluesky',
                    site_data,
                    coverage_data)
```

### malaria-rts3-rts4-default

```{r}
incidence_over_time(burden_output$by_year, 
                    scenario= 'malaria-rts3-rts4-default',
                    site_data,
                    coverage_data)
```

### malaria-rts3-rts4-bluesky

```{r}
incidence_over_time(burden_output$by_year, 
                    scenario= 'malaria-rts3-rts4-bluesky',
                    site_data,
                    coverage_data)
```

## Cases averted over time {.tabset}

### malaria-rts3-bluesky

```{r}
cases_averted_over_time(averted_output$by_year, 
                        scenario= 'malaria-rts3-bluesky',
                        country_name = {{country_name}})
```

### malaria-rts3-default

```{r}
cases_averted_over_time(averted_output$by_year, 
                        scenario= 'malaria-rts3-default',
                        country_name = {{country_name}})
```

### malaria-rts3-rts4-bluesky

```{r}
cases_averted_over_time(averted_output$by_year, 
                        scenario='malaria-rts3-rts4-bluesky',
                        country_name = {{country_name}})
```

### malaria-rts3-rts4-default

```{r}
cases_averted_over_time(averted_output$by_year, 
                        scenario= 'malaria-rts3-rts4-default',
                        country_name = {{country_name}})
```

## Cases averted over age {.tabset}

### malaria-rts3-bluesky

```{r}
cases_averted_over_age(averted_output$by_age, 
                        scenario= 'malaria-rts3-bluesky',
                        country_name = {{country_name}})
```

### malaria-rts3-default

```{r}
cases_averted_over_age(averted_output$by_age, 
                        scenario= 'malaria-rts3-default',
                        country_name = {{country_name}})
```

### malaria-rts3-rts4-bluesky

```{r}
cases_averted_over_age(averted_output$by_age, 
                        scenario='malaria-rts3-rts4-bluesky',
                        country_name = {{country_name}})
```

### malaria-rts3-rts4-default

```{r}
cases_averted_over_age(averted_output$by_age, 
                        scenario= 'malaria-rts3-rts4-default',
                        country_name = {{country_name}})
```

## Incidence over age {.tabset}

### malaria-rts3-default

```{r}
incidence_over_age(burden_output$by_age, 
                    scenario= 'malaria-rts3-default',
                    coverage_data)
```

### malaria-rts3-bluesky

```{r}
incidence_over_age(burden_output$by_age, 
                    scenario= 'malaria-rts3-bluesky',
                    coverage_data)
```

### malaria-rts3-rts4-default

```{r}
incidence_over_age(burden_output$by_age, 
                    scenario= 'malaria-rts3-rts4-default',
                    coverage_data)
```

### malaria-rts3-rts4-bluesky

```{r}
incidence_over_age(burden_output$by_age, 
                    scenario= 'malaria-rts3-rts4-bluesky',
                    coverage_data)
```

# Deaths

## Deaths over time {.tabset}

### malaria-rts3-default

```{r}
deaths_over_time(burden_output$by_year, 
                    scenario= 'malaria-rts3-default',
                    coverage_data)
```

### malaria-rts3-bluesky

```{r}
deaths_over_time(burden_output$by_year, 
                    scenario= 'malaria-rts3-bluesky',
                    coverage_data)
```

### malaria-rts3-rts4-default

```{r}
deaths_over_time(burden_output$by_year, 
                    scenario= 'malaria-rts3-rts4-default',
                    coverage_data)
```

### malaria-rts3-rts4-bluesky

```{r}
deaths_over_time(burden_output$by_year, 
                    scenario= 'malaria-rts3-rts4-bluesky',
                    coverage_data)
```

## Deaths over age {.tabset}

### malaria-rts3-default

```{r}
deaths_over_age(burden_output$by_age, 
                    scenario= 'malaria-rts3-default',
                    coverage_data)
```

### malaria-rts3-bluesky

```{r}
deaths_over_age(burden_output$by_age, 
                    scenario= 'malaria-rts3-bluesky',
                    coverage_data)
```

### malaria-rts3-rts4-default

```{r}
deaths_over_age(burden_output$by_age, 
                    scenario= 'malaria-rts3-rts4-default',
                    coverage_data)
```

### malaria-rts3-rts4-bluesky

```{r}
deaths_over_age(burden_output$by_age, 
                    scenario= 'malaria-rts3-rts4-bluesky',
                    coverage_data)
```

## Deaths averted over time {.tabset}

### malaria-rts3-bluesky

```{r}
deaths_averted_over_time(averted_output$by_year, 
                        scenario= 'malaria-rts3-bluesky',
                        country_name = {{country_name}})
```

### malaria-rts3-default

```{r}
deaths_averted_over_time(averted_output$by_year, 
                        scenario= 'malaria-rts3-default',
                        country_name = {{country_name}})
```

### malaria-rts3-rts4-bluesky

```{r}
deaths_averted_over_time(averted_output$by_year, 
                        scenario='malaria-rts3-rts4-bluesky',
                        country_name = {{country_name}})
```

### malaria-rts3-rts4-default

```{r}
deaths_averted_over_time(averted_output$by_year, 
                        scenario= 'malaria-rts3-rts4-default',
                        country_name = {{country_name}})
```

## Deaths averted over age {.tabset}

### malaria-rts3-bluesky

```{r}
deaths_averted_over_age(averted_output$by_age, 
                        scenario= 'malaria-rts3-bluesky',
                        country_name = {{country_name}})
```

### malaria-rts3-default

```{r}
deaths_averted_over_age(averted_output$by_age, 
                        scenario= 'malaria-rts3-default',
                        country_name = {{country_name}})
```

### malaria-rts3-rts4-bluesky

```{r}
deaths_averted_over_age(averted_output$by_age, 
                        scenario='malaria-rts3-rts4-bluesky',
                        country_name = {{country_name}})
```

### malaria-rts3-rts4-default

```{r}
deaths_averted_over_age(averted_output$by_age, 
                        scenario= 'malaria-rts3-rts4-default',
                        country_name = {{country_name}})
```

# DALYs

## DALYs over time {.tabset}

### malaria-rts3-default

```{r}
dalys_over_time(burden_output$by_year, 
                    scenario= 'malaria-rts3-default',
                    coverage_data)
```

### malaria-rts3-bluesky

```{r}
dalys_over_time(burden_output$by_year, 
                    scenario= 'malaria-rts3-bluesky',
                    coverage_data)
```

### malaria-rts3-rts4-default

```{r}
dalys_over_time(burden_output$by_year, 
                    scenario= 'malaria-rts3-rts4-default',
                    coverage_data)
```

### malaria-rts3-rts4-bluesky

```{r}
dalys_over_time(burden_output$by_year, 
                    scenario= 'malaria-rts3-rts4-bluesky',
                    coverage_data)
```

## DALYs averted over age {.tabset}

### malaria-rts3-bluesky

```{r}
dalys_averted_over_age(averted_output$by_age, 
                        scenario= 'malaria-rts3-bluesky',
                        country_name = {{country_name}})
```

### malaria-rts3-default

```{r}
dalys_averted_over_age(averted_output$by_age, 
                        scenario= 'malaria-rts3-default',
                        country_name = {{country_name}})
```

### malaria-rts3-rts4-bluesky

```{r}
dalys_averted_over_age(averted_output$by_age, 
                        scenario='malaria-rts3-rts4-bluesky',
                        country_name = {{country_name}})
```

### malaria-rts3-rts4-default

```{r}
dalys_averted_over_age(averted_output$by_age, 
                        scenario= 'malaria-rts3-rts4-default',
                        country_name = {{country_name}})
```

## DALYs averted over time {.tabset}

### malaria-rts3-bluesky

```{r}
dalys_averted_over_time(averted_output$by_year, 
                        scenario= 'malaria-rts3-bluesky',
                        country_name = {{country_name}})
```

### malaria-rts3-default

```{r}
dalys_averted_over_time(averted_output$by_year, 
                        scenario= 'malaria-rts3-default',
                        country_name = {{country_name}})
```

### malaria-rts3-rts4-bluesky

```{r}
dalys_averted_over_time(averted_output$by_year, 
                        scenario='malaria-rts3-rts4-bluesky',
                        country_name = {{country_name}})
```

### malaria-rts3-rts4-default

```{r}
dalys_averted_over_time(averted_output$by_year, 
                        scenario= 'malaria-rts3-rts4-default',
                        country_name = {{country_name}})
```
